Scalar on Function Regression \\ with Applications to Near-Infrared Spectography

### 2022-01-13 Presentation/slides.tex
update
Added bibliography

	\begin{frame}{Random Function}
		Let $\mathbb{E}$ be the index set and this can be described as
		$${\{X(t,\omega) : t \in \mathbb{E}, \omega \in \Omega\},}$$
		where $X(t, \cdot)$ is $\mathcal{F}$-measurable function on the sample space $\Omega$.\\
		\begin{itemize}
			\item It can be shortened to $X(t)$ by omitting $\omega$
			\item The function is realized when the $X(t)$ exists $\forall t \in \mathbb{E}$
		\end{itemize}
	\end{frame}

@@

	\begin{frame}{Square Integrable Function}
		If a function $f(t)$ satisfies
		$$\int_{0}^{1} \left(f(t)\right)^{2}dt < \infty$$
		the function $f(t)$ is called \textbf{Square Integrable Function} written $f(t) \in \mathbb{L}^{2}[0,1]$.
		\begin{itemize}
			\item Without loss of generality, the interval is defined in $[0,1] $
			\item $\mathbb{L}^{2}$ is the set of all square integrable functions
			\item We focus on $\mathbb{L}^{2} [0,1]$ since the domain of our function is on the real line.
		\end{itemize}
	\end{frame}

	\begin{frame}{Square Integrable Function}
		Let $f, g \in \mathbb{L}^{2}[0,1]$, then
		%$$(ab + bg)(t) = af(t) + bg(t), \quad t \in [0,1] and \forall a,b$$
		%, where $a$ and $b$ are scalars. (Maybe don't need)\\
		%We can additionally define the inner product as follows:
		$$\langle f,g \rangle = \int_{0}^{1} f(t)g(t)dt$$
		%\begin{itemize}
		%	\item 
		Orthogonality of two different functions $\langle f,g \rangle = 0$
			%\item Distance between functions
		%\end{itemize}
	\end{frame}

@@

	\begin{frame}{Basis Expansion}
		\textbf{Basis Expansion} is a linear combination of functions defining a function as described:
		$$X_{i}(t) = \sum_{k=1}^{\infty} c_{ik}\phi_{k}(t) \approx \sum_{k=1}^{K} c_{ik}\phi_{k}(t), \quad i = 1, \dots, n, \quad \forall t \in \mathbb{E}$$
		where $\phi_{k}(t)$ is the $k^{th}$ basis function of the expansion and $c_{ik}$ is the corresponding coefficient. We truncate the basis at $K$ to:
		\vspace{0.2cm}

@@

	\begin{frame}{Two Typical Types of Basis Function}
		\textbf{Fourier Basis Function} is written as
		$$f(x) = a_{0} + \sum_{n=1}^{\infty}a_{n}cos(2\pi nx) + b_{n}sin(2\pi nx)$$	\\
		\vspace{2\baselineskip}
		\textbf{B-spline Basis Function} is a flexible curve defined by degree and knots. \\
		Each B-spline basis function, $i$-th B-spline basis function of degree $p$, $N_{i,p}(u)$ is defined on Cox-de Boor recursion formula.
	\end{frame}

	\begin{frame}{Plots of Basis Functions}
		\begin{figure}
			\includegraphics[height = 4.5cm]{../Graphics/Fourier_Basis.pdf}
			\caption {Fourier basis functions with order 9}
		\end{figure}

@@

	\begin{frame}{Plots of Basis Functions}
		\begin{figure}
			\includegraphics[height = 4.5cm]{../Graphics/Bspline_Basis.pdf}
			\caption {Bspline basis functions with order 9}
		\end{figure}
	\end{frame}

	\begin{frame}{Trade Off between Bias and Variance}
		How do we choose the number $K$ of basis functions?
		$$\textbf{MSE}[\hat{x}(t)] = \textbf{Bias}^2[\hat{x}(t)] + \textbf{Var}[\hat{x}(t)]$$

		{\color{red} Integrated Mean Squared Error}
		\begin{itemize}
			\item The larger $K$, the better fit to the data with also fitting noise
			\item If $K$ is too small, it would miss some significant information that we want to estimate 
		\end{itemize}
	\end{frame}

@@

	\begin{frame}{Further Reading}
		 Put footnotes here!
		 Yuanpeng Li et al.(2020): Early Diagnosis of Type 2 Diabetes Based on Near-Infrared Spectroscopy Combined With Machine Learning and Aquaphotomics, Frontiers of Chemistry (8)
	\end{frame}

>>>>

	\begin{frame}{Random Function}
		Let $\mathbb{E}$ be the index set and this can be described as
		$${X = \{X(t,\omega) : t \in \mathbb{E}, \omega \in \Omega\},}$$
		where $X(t, \cdot)$ is $\mathcal{F}$-measurable function on the sample space $\Omega$.\\
		\begin{itemize}
			\item It can be shortened to $X(t)$ by omitting $\omega$
			\item The function is realized when the $X(t)$ exists $\forall t \in \mathbb{E}$
		\end{itemize}
	\end{frame}

@@

	\begin{frame}{Square Integrable Function}
		If a function $f(t)$ satisfies
		$$\int_{0}^{1} \left(f(t)\right)^{2}dt < \infty$$
		the function $f(t)$ is called \textbf{Square Integrable Function} written $f(t) \in \mathbb{L}^{2}[0,1]$.
		\begin{itemize}
			\item Without loss of generality, the interval is defined in $[0,1]$.
			\item $\mathbb{L}^{2}$ is the set of all square integrable functions.
		\end{itemize}
	\end{frame}

	\begin{frame}{Square Integrable Function}
		Let $f, g \in \mathbb{L}^{2}[0,1]$, then we can define inner product by
		%$$(ab + bg)(t) = af(t) + bg(t), \quad t \in [0,1] and \forall a,b$$
		%, where $a$ and $b$ are scalars. (Maybe don't need)\\
		%We can additionally define the inner product as follows:
		$$\langle f,g \rangle = \int_{0}^{1} f(t)g(t)dt$$
		%\begin{itemize}
		%	\item
		\begin{itemize}
			\item Orthogonality of two different functions with $\langle f,g \rangle = 0$
			\item Distance between functions
		\end{itemize}
	\end{frame}

@@

	\begin{frame}{Basis Expansion}
		\textbf{Basis Expansion} is a linear combination of functions as described:

		$$X_{i}(t) = \sum_{k=1}^{\infty} c_{ik}\phi_{k}(t) \approx \sum_{k=1}^{K} c_{ik}\phi_{k}(t), \quad i = 1, \dots, n, \quad \forall t \in \mathbb{E}$$

		where $\phi_{k}(t)$ is the $k^{th}$ basis function of the expansion and $c_{ik}$ is the corresponding coefficient. We truncate the basis at $K$ to:
		\vspace{0.2cm}

@@

	\begin{frame}{Two Typical Types of Basis Function}
		\textbf{Fourier Basis Function} is an element of the set:

		$$\{\sqrt{2}sin(2\pi nx | n \in \mathbb{N})\} \cup \{\sqrt{2}cos(2\pi nx | n \in \mathbb{N})\} \cup \{1\}$$

		%$$f(x) = a_{0} + \sum_{n=1}^{\infty}a_{n}cos(2\pi nx) + b_{n}sin(2\pi nx)$$	\\

		\vspace{2\baselineskip}
		\textbf{B-spline Basis Function} is a polynomial function defined by order and knots. \\

@@

	\begin{frame}{Plots of Basis Functions}
		\begin{figure}
			\includegraphics[height = 4.5cm]{../Graphics/Fourier_Basis.pdf}
			\caption {Fourier basis functions}
		\end{figure}

	\begin{frame}{Plots of Basis Functions}
		\begin{figure}
			\includegraphics[height = 4.5cm]{../Graphics/Bspline_Basis.pdf}
			\caption {Bspline basis functions}
		\end{figure}
	\end{frame}

	\begin{frame}{Trade Off between Bias and Variance}
		How do we choose the number $K$ of basis functions?

		$$\textbf{MSE}[\hat{X}(t)] = \textbf{Bias}^2[\hat{X}(t)] + \textbf{Var}[\hat{X}(t)]$$

		$$\textbf{MISE}[\hat{X}] = \int_{0}^{1} \textbf{MSE}[\hat{X}(t)] dt$$

		\begin{itemize}
			\item The larger $K$, the better fit to the data with also fitting noise
			\item If $K$ is too small, it would miss some significant information
		\end{itemize}
	\end{frame}

@@

	\begin{frame}{Further Reading}
		 Further Reading:
		 \nocite{Bohacs_Ovadi_Salgo1998}
		 \nocite{FR_li_et_al_2020} 
		 \nocite{Reiss_2007b}
		 \AtNextBibliography{\tiny}
		 \printbibliography[heading=none]
	\end{frame}
